Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-02-23 Thesis/01-chap1.Rmd
add sample size calc

>>>>

## Sample Size Calculation

In this study, multiple selection was allowed for the evaluation of a lineup. Given our desired significance level was $\alpha = 0.05$ and the number of plots in a lineup was $20$, a single visual test procedure needed to involve multiple evaluations. Otherwise, there would be a high chance that the $p$-value of the test was greater than $0.05$ in spite of the actual data plot was selected. The number of plots selected by a user depended on the user and the difficulty of the lineup. But according to our pilot study ran in a small group, the number would be generally smaller than $5$. Hence, a visual test consisted of $5$ lineups were sufficient to yield $p$-value smaller than $0.004$. Thus, each lineup would be replicated for $5$ times and evaluated by different participants. However, our study website was designed such that any set of lineups would be shown to only one person only once. A set of lineups consists 20 lineups generated before the start of the study. Further, whether the participant would finish the experiment was unpredictable. Therefore, some lineups only had $2$ evaluations but some had as large as $8$ evaluations. This slightly affected the estimate of the power of the visual test, which would be discussed in the (section here).

Besides, the sample size calculation was based on the difficulty of the lineup. With the data collected from the pilot study, two generalized linear model (GLM) model was developed to describe the relationship between the effect size and the detection rate.

### 2022-02-23 Thesis/_book/thesis.tex
add sample size calc

>>>>

\hypertarget{sample-size-calculation}{%
\section{Sample Size Calculation}\label{sample-size-calculation}}

In this study, multiple selection was allowed for the evaluation of a lineup. Given our desired significance level was \(\alpha = 0.05\) and the number of plots in a lineup was \(20\), a single visual test procedure needed to involve multiple evaluations. Otherwise, there would be a high chance that the \(p\)-value of the test was greater than \(0.05\) in spite of the actual data plot was selected. The number of plots selected by a user depended on the user and the difficulty of the lineup. But according to our pilot study ran in a small group, the number would be generally smaller than \(5\). Hence, a visual test consisted of \(5\) lineups were sufficient to yield \(p\)-value smaller than \(0.004\). Thus, each lineup would be replicated for \(5\) times and evaluated by different participants. However, our study website was designed such that any set of lineups would be shown to only one person only once. A set of lineups consists 20 lineups generated before the start of the study. Further, whether the participant would finish the experiment was unpredictable. Therefore, some lineups only had \(2\) evaluations but some had as large as \(8\) evaluations. This slightly affected the estimate of the power of the visual test, which would be discussed in the (section here).

Besides, the sample size calculation was based on the difficulty of the lineup. With the data collected from the pilot study, two generalized linear model (GLM) model was developed to describe the relationship between the effect size and the detection rate.
